---
title: "Untitled"
author: "Anna Talucci"
date: "10/18/2020"
output: html_document
---
# Overview

Re-define projections

# Packages
```{r, include=FALSE}
library(sp) # spatial data
library(rgdal) # geospatial data
library(raster) # deals with rasters
library(ggplot2)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(tidyr)
library(dplyr)
library(latticeExtra)
library(sf)
```

# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 
+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 "
```


# Reproject
Transform to Equal area projection
**Replace VECTOR_WGS with YOUR POINT SHAPEFILE**
**Rename VECTOR_ee as you see fit**
**VECTOR_ee linked through script**
```{r}
VECTOR_ee <- spTransform(VECTOR_WGS, CRS(ee_russia))
```

Transform from sp object to sf object in order to save to shapefile (sf objects allow for attribute tables and using tidyverse package)
```{r}
VECTOR_ee_sf = st_as_sf(VECTOR_ee)
```

## Write to shape file

**I use a subdirectory folder structure folder structurethat keeps scripts, data, outputs, figures in separate folders**
**This chunk of code is set up to go to a subfolder for outputs**
**this portion indicates the subfolder and file name "../outputs/field-data/point/VECTOR_ee_sf.shp"**
```{r eval=FALSE, include=FALSE}
st_write(VECTOR_ee_sf, "../outputs/field-data/point/VECTOR_ee_sf.shp", driver="ESRI Shapefile") 